resistanceModelNotesAndy

### 2015-06-04 resistanceModelNotesAndy.Rmd
progress notes

to do with object genotype ....
Aha! problems were due to my new sex-linked changes that were operating without me realising.
So I should probaly remove the tolerances I put in. and work out how to reassign the impossible genotype freqs.

@@

1. check on implementation of sexLinkage in randomMating()

1. think I can remove genotype.freq it is the same as f['m',], I might want to create an fstart[] outside of the generations loop. This was prompted because previously genotype.freq was the same for males and females and it adds an unecessary extra layer of potential confusion

1. further develop sex-linkage in randomMating(), allow option to be passed as arg, plus may need to look at calculating genotypes of both m&f in runModel2()

@@

1. Maybe create a model diagram perhaps from diagrammer ?

>>>>

to do with object genotype ....
Aha! problems were due to my new sex-linked changes that were operating without me realising.
So I should probaly remove the tolerances I put in. and work out how to reassign the impossible genotype freqs.
done

**4/6/15** thurs 12.15-

checking on implementation of sexLinkage in randomMating()

sexLinked probably needs to be included as an extra paramter in input (but should make it robust to cope if an input file doesn't have the sex-linked option)

be careful because this could break previous model runs

genotype.freq mostly removed it was the same as f['m',]. Creation of f & fs moved to before the generations loop. This was prompted because previously genotype.freq was the same for males and females and it adds an unecessary extra layer of potential confusion.

added calculating genotypes of both m&f in runModel2() to allow sex linkage.

bug in random mating with sex linkage genotypes aren't summing to 1

fGenotypeExpanded for non sex-linked looks like the top one
In the lower one the R1 homozgotes should sum to 1 too

    l1a2
l1a1     S1     R1
  S1 0.0625 0.0625
  R1 0.0625 0.0625

    l1a2
l1a1    S1     R1
  S1 0.125 0.0000
  R1 0.000 0.0625

Fixed now :
with this bit of code :
```
#heterozygotes at locus1 are impossible so add to the homozygotes instead
if(f1!=m1)
{
  #add to the homozygotes : f1,f1
  fGenotypeExpanded[f1,f1,f2,m2] <- fGenotypeExpanded[f1,f1,f2,m2] + fThisGenotype
} else #i.e. if not heterozygous at locus 1
{
  #just add to this genotype : f1,m1
  #have to add rather than set in case this is a homozygote that has already been added to by previous condition
  fGenotypeExpanded[f1,m1,f2,m2] <- fGenotypeExpanded[f1,m1,f2,m2] + fThisGenotype
}
```

Created a new shiny app in shinyCurtis2 and run from runUI2.R to look at graphs with & without sex linkage side by side. Initially these gave identical results, which was because resistSimple() called the old runModel() which doesn't allow sex linkage. Try it again now.

Cool, now I am getting a difference between locus1 & locus2. However males & females still have the same results, is that what would be expected ?

Maybe it's because of the way that results are output from Beths one sex system ?
Where does the graph get the data from ?

genplot <- plotallele.freq.andy( listOut$results[[1]] )

  # Males
  lines( mat[,1], mat[,2], col="darkblue", lwd=2, lty=13 )
  lines( mat[,1], mat[,3], col="green", lwd=2, lty=14 )
  # Females
  lines( mat[,1], mat[,5], col="red",lwd=2, lty=15 )
  lines( mat[,1], mat[,6], col="orange", lwd=2, lty=16 )

so its columns 2,3,5 & 6 I'm interested in

so where is listOut$results[[1]] filled ?
in runModel2()     listOut$results[[i]] <- results
& further back :
```
      ## frequency of resistance alleles
      m.R1 <- sum(f['m',grep("RR1",colnames(f))]) + ( 0.5 * sum(f['m',grep("RS1",colnames(f))]))
      m.R2 <- sum(f['m',grep("RR2",colnames(f))]) + ( 0.5 * sum(f['m',grep("RS2",colnames(f))]))
      f.R1 <- sum(f['f',grep("RR1",colnames(f))]) + ( 0.5 * sum(f['f',grep("RS1",colnames(f))]))
      f.R2 <- sum(f['f',grep("RR2",colnames(f))]) + ( 0.5 * sum(f['f',grep("RS2",colnames(f))]))   
      results[k,2] <- m.R1
      results[k,3] <- m.R2
      results[k,5] <- f.R1
      results[k,6] <- f.R2
```

Seems that this should be doing the right thing. Maybe the allele frequencies overall don't change, because for the males they just redistributed from heterozygotes to homozygotes.

@@

1. be careful that runModel & runModel2 should no longer generate same results when sex linkage is set (but i don't think this should break current testthat tests)

@@
